
```{r starwars_read, eval=T}
#install.packages("readr")
library(readr)

read_csv("https://itep-r.netlify.com/data/starwars_scrap_jakku.csv")
```


## Name the data {-}

Where did the data go after you read it into R? When we want to work with the data in R, we need to give it a name with the assignment operator: `<-`. 

```{r starwars_csv_name, eval=T, message=F}
# Read in scrap data and set name to "scrap"
scrap <- read_csv("https://itep-r.netlify.com/data/starwars_scrap_jakku.csv")

# Type the name of the table to view it in the console
scrap
```

<br>


<div class="tip">
### <i class="fas fa-hand-spock"></i> Spock-tip! {-}

Notice the row of `<three>` letter abbreviations under the column names? These describe the data type of each column.

- `<chr>` stands for __character__ vector or a string of characters. Examples: _"apple"_, _"apple5"_, _"5 red apples"_  
- `<int>` stands for __integer__. Examples: _5_, _34_, _1071_  
- `<dbl>` stands for __double__. Examples: _5.0000_, _3.4E-6_, _10.7106_

We'll explore more data types later on, such as `dates` and `logical` (TRUE/FALSE).
</div>


<div class="quiz">

<h2 style="margin-top: 28px; margin-bottom: 44px;"> Pop Quiz! </h2>

__1. What data type is the `destination` column?__

<input type="radio" name="type"> _letters_        <br> 
<input type="radio" name="type"> _character_      <br> 
<input type="radio" name="type"> _TRUE/FALSE_     <br> 
<input type="radio" name="type"> _numbers_        <br> 

<details style="margin-left: 14px;">
<summary class = "btn_code">_Show solution_</summary>
<p>
<i class="fa fa-check" aria-hidden="true" style="color: green;"></i> `character`    
_Woop! You got this._
</p></details>

<br>
<hr style="margin-top: 8px;">

__2. What package does `read_csv()` come from?__

<input type="radio" name="pkg"> _dinosaur_     <br> 
<input type="radio" name="pkg"> _get_data_     <br> 
<input type="radio" name="pkg"> _readr_        <br> 
<input type="radio" name="pkg"> _dplyr_        <br> 

<details style="margin-left: 14px;">
<summary class = "btn_code">_Show solution_ </summary>
<p>

<i class="fa fa-check" aria-hidden="true" style="color: green;"></i> `readr`  
_Great job! You are Jedi worthy!_

</p></details>

<br>
<hr style="margin-top: 8px;">

__3. How would you load the package `junkfinder`?__

<input type="radio" name="load"> _junkfinder()_             <br> 
<input type="radio" name="load"> _library(junkfinder)_      <br> 
<input type="radio" name="load"> _load(junkfinder)_         <br> 
<input type="radio" name="load"> _gogo_gadget(junkfinder)_  <br> 

<details style="margin-left: 14px;">
<summary class = "btn_code">_Show solution_</summary>
<p>

<i class="fa fa-check" aria-hidden="true" style="color: green;"></i> `library("junkfinder")`  
_Excellent! Keep the streak going._

</p></details>

</div>

<br>
