---
title: "Air, wind and roses"
output: 
  blogdown::html_page: 
    toc: false
    toc_depth: 2
    highlight: tango
    css: css/camp_style.css
    number_sections: false
    self_contained: false
    fontsize: 18pt
    monofont: Source Code Pro
---


Let's take a look at some air pollution data stored in an Excel file.

## Download the data

<a href="https://itep-r.netlify.com/data/la_jolla_pm25_wind_data.xls">
<span class = "btn_code_blue"> __DOWNLOAD__  </span></a> —  La Jolla PM25 data


## Install packages
```{r, eval=F}

# Get devtools for installing new packages from GitHub
install.packages("devtools", dependencies = TRUE)

# Load the devtools library 
library(devtools)

# Install openair for windrose functions
install_github('davidcarslaw/openair')
```


## Load the data
```{r, warning=F, message=F}

# Load packages
library(openair)
library(readxl)
library(ggplot2)
library(dplyr)
library(lubridate)

# Set the path to your the Excel file
excel_path <- "data/la_jolla_pm25_wind_data.xls"
```

```{r, include=F, echo=F}
excel_path <- "../data/la_jolla_pm25_wind_data.xls"
#excel_path <- "../data/2014_AQS_FondduLac.xlsx"

if(F) {
air_data <- air_data %>% 
            rename(wind_dir   = "Wind Direction (Degrees)",
                   wind_mph   = "Wind Speed (mph)",
                   pm25       = "PM2.5 Conc (ug/m3)") %>%
            rename_all(tolower)

}

```

```{r}
# Read the file
air_data <- read_excel(excel_path)
```

## Explore the data

What are the column names? 

```{r, eval=F}

names(air_data)

glimpse(air_data)

summary(air_data)

```



## Simplify the column names
```{r}

# Drop special characters and shorten names
# Set all names to lowercase
air_data <- air_data %>% 
            rename(pm25 = "PM2.5 Conc (ug/m3)", 
                   wd   = "Wind Direction (Degrees)",
                   ws   = "Wind Speed (mph)") %>%
            rename_all(tolower)

# We need numbers for our data, not text
# Set wind speed and wind direction to numeric
air_data <- air_data %>% 
            mutate(wd   = as.numeric(wd),
                   ws   = as.numeric(ws))

```


## Plot the data

Create a plot to show the distribution of each of the columns containing observations: `wind speed`, `wind direction`, and `concentration`.


```{r, eval=F}

ggplot(air_data, aes(x = ?, y = ?)) + geom_point()


```

## Clean ship

Let's drop the non-sense values. We can't use the rows that have a missing windspeed or wind direction observation.

```{r, eval=T}
air_data <- filter(air_data, 
                   !is.na(ws), 
                   !is.na(wd),
                   !is.na(pm25),
                   ws > 0)
```

## Wind rose

Now let's make some wind roses.

```{r, eval=T}

# Plot the data
windRose(air_data)

polarFreq(air_data)
```

```{r, eval=F}
#-- Fine tune  wind rose
polarFreq(air_data, ws.int =5, ws.upper = 35)

polarFreq(air_data, ws.int =0.8, breaks = seq(2:30))

```


## Pollution rose

To make a pollution rose we can replace the name of the wind speed column with the name of PM2.5 column - `"PM2.5 Conc (ug/m3)"`

```{r, eval=T}

# Pollution concentrations based on wind directions
pollutionRose(air_data, 
              pollutant = "pm25",
              key.footer = "PM2.5 ug/m3")
              
```



## Time series

<a href="https://github.com/itep-data/learnR/raw/master/content/data/2014_AQS_FondduLac.xlsx">
<span class = "btn_code_blue"> __DOWNLOAD__  </span></a> —  Ozone air data

```{r, eval=F}
library(lubridate)
library(readr)
library(ggplot2)

# Read the file
excel_path <- "data/2014_AQS_FondduLac.xlsx"

air_data <- read_excel(excel_path)
```

```{r, echo=F}
# Read the file
excel_path <- "../data/2014_AQS_FondduLac.xlsx"

air_data <- read_excel(excel_path)

head(air_data, 5)
```


## Explore the data
```{r, eval=F}

names(air_data)

glimpse(air_data)
```


## Simplify the column names
```{r}

# Set all names to lowercase
air_data <- air_data %>% 
            rename_all(tolower) %>%
            rename(site = site_catid)

```

## Let's focus on PM2.5

Use filter to select only the `parameter` code `88101`.

```{r, eval=F}

air_data <- filter(air_data, parameter == ??)
```


```{r}

air_data <- filter(air_data, parameter == 88101)
```



Let's summarize the observations by day and then make a time series chart to see how the pollution concentrations are changing over time.

__Add monthly statistics__
```{r}

# Add a month column
air_data <- air_data %>% 
            mutate(day   = day(date),
                   month = month(date),
                   year  = year(date))


# Find average PM25 concentration for each day
#   - And upper and lower 10th percentile concentration
air_summary <- group_by(air_data, site, year, month, day, date) %>%
               summarize(conc_avg  = mean(conc, na.rm = T),
                         conc_10th = quantile(conc, 0.10, na.rm = T),
                         conc_90th = quantile(conc, 0.90, na.rm = T)) %>%
               ungroup()


```


__Plot a line chart__
```{r}

ggplot(air_summary, aes(x = date, y = conc_avg)) +
   geom_line() +
   facet_wrap(~ site)

```


Now we can add a confidence band behind the line showing the upper and lower 10th percentile of the observations.

```{r}

ggplot(air_summary, aes(x = date, y = conc_avg)) + 
   geom_smooth(method ="loess", level = 0.90) +
   geom_line(color = "tomato") +
   facet_wrap(~site)

```


__What happens when you increase the `level = 0.90` up to `0.999`, making the shaded band a 99% confidence interval?__

__Try adding another confidence band, but make it a linear model: `method = "lm"`, and set the color to "black". Does the new line predict the concentration to be going down or up at each site?__


```{r}

ggplot(air_summary, aes(x = date, y = conc_avg)) + 
   geom_smooth(method = "loess", level = 0.999) +
   geom_line(color = "tomato") +
   geom_smooth(method = "lm", level = 0.90, color = "black") +
   facet_wrap(~site)

```

<br>

### <i class="fa fa-rocket" aria-hidden="true"></i> Return to [Day 3-AM](day3_am.html) {-}

<br>


<br>
