

Let's apply our new `left_join()` skills to the scrap data.

First, let's re-read the full scrap data.
```{r join-convert, eval=T}
library(readr)
library(dplyr)

# Read in the larger scrap database
scrap <- read_csv("https://itep-r.netlify.com/data/starwars_scrap_jakku_full.csv")

# what units types are in the data? 
distinct(scrap, units)
```


### Join the conversion table to scrap {-}

Look at the tables. What columns in both tables do we want to join __by__?
```{r, eval=F}
names(scrap)
```

Let's join by `item` and `units`.
```{r, eval=T}
# Join the scrap to the conversion table
scrap <- left_join(scrap, convert, 
                   by = c("item"  = "item", 
                          "units" = "units"))
```

<br>

> __Want to save on typing?__

`left_join()` will automatically search for matching columns if you don't use the `by=` argument. So if you know 2 tables share a column name you don't have to specify how to join them. The code below does the same as above.

```{r join-convert2, eval=F}
scrap <- left_join(scrap, convert)

head(scrap, 4)
```

```{r join-convert3, eval=T, echo=F}
head(scrap, 4)
```


<div class="quiz">
### __Help!__ {-}

For more details, you can type `?left_join` to see all the arguments and options.
<br>
</div>
