
Use these functions to describe your data.

### Data frame info {-}

<div class="pinkcode">

| Function  |  | Information                                                      |   
|:----------|--|:-----------------------------------------------------------------|
| `names(scrap)`  |  | column names            |  
| `nrow(...)`     |  | number of rows          |  
| `ncol(...)`     |  | number of columns       | 
| `summary(...)`  |  | summary of all column values (ex. _max_, _mean_, _median_)  | 
| `glimpse(...)`  |  | column names + a glimpse of first values (requires _dplyr_ package)   |

</div>


# `glimpse()` & `summary()`
<hr>



### Let's read the scrap data into R and take a look. {-}

```{r read-glimpse, warning=F, message=F}
library(readr)
library(dplyr)

scrap <- read_csv("https://mn-r.netlify.com/data/starwars_scrap_jakku.csv")
```

<br>

`glimpse()` shows you the type of data you have and gives you a sample of values from each column.

```{r glimpse-sc, warning=F, message=F}
# View your whole dataframe and the types of data it contains
glimpse(scrap)
```

<br>

`summary()` gives you a quick report of your numeric data.

```{r summary-scrap, warning=F, message=F}
# Summary gives us the means, mins, and maxima 
summary(scrap)
```

<br>

<div class="tip">
### <i class="fas fa-user-astronaut" aria-hidden="true" style="color: green"></i> Explore! {-}

Try some more of the dataframe description functions.

```{r summary-try, eval=F}
nrow( ____ )

ncol( ____ )

names( ____ )
```

</div>

