
To help find the junk we need for our ship we're going to conduct a scrap audit. The first step of a good audit is reading in data determine where all the scrap is coming from. 

Here's a small dataset showing the scrap economy on Jakku. It was salvaged from a crash site, but the transfer was incomplete.

```{r ex-data1, echo=F, message=F, warning=F}
library(readr)
library(tibble)
library(knitr)

options(scipen = 999)

scrap <- data.frame(origin      = c("Outskirts", "Niima Outpost", "Cratertown", "Tro----"), 
                    destination = c("Raiders", "Trade caravan", "Plutt", "Ta----"), 
                    item        = c("Bulkhead", "Hull panels", "Hyperdrives", "So---*"), 
                    amount      = c(332, 1120, 45, 1), 
                    price_d     = c("300", "286", "45", "10----"))

kable(scrap)
```


This looks like it could be useful. Now, if only we had some more data to work with...

## New Message {-}

<details>
<summary class = "btn_code_green">_Incoming..._ _BB8_</summary>
<p>

<div class="tip">
__BB8:__ _Beep boop Beep._

__BB8:__ _I intercepted a large scrapper data set from droid 4P-L of Junk Boss Plutt._   

<br>

Receiving data now...

__scrap_records.csv__ 

```{r, eval=F}
item,origin,destination,amount,units,price_per_pound  
Flight recorder,Outskirts,Niima Outpost,887,Tons,590.93  
Proximity sensor,Outskirts,Raiders,7081,Tons,1229.03  
Aural sensor,Tuanul,Raiders,707,Tons,145.27  
Electromagnetic filter,Tuanul,Niima Outpost,107,Tons,188.2  
...  
```

<br>

__You:__ _Yikes! This looks like a dense mess! What can I do with this?_

</div>
</p></details>


## CSV to the rescue {-}

The main data format used in R is the __CSV__ _(comma-separated values)_. A __CSV__ is a simple text file that can be opened in R and most other data tools, including Excel. It looks squished together as plain text, but that's okay! When opened in R, the text becomes a familiar looking table with columns and rows. 

Before we launch ahead, let's add a _package_ to R that will help us read __CSV__ files.

<br>
