
`mutate() ` can edit existing columns in a data frame or add new values that are calculated from existing columns.


## Add a column {-}

First, let's add a column with our names. That way Rey can thank us personally when her ship is finally up and running. 
```{r mutate-1, warning=F, message=F}
# Add your name as a column
scrap <- mutate(scrap, scrap_finder = "BB8")

```


## Add several columns {-}

Let's also add a new column to document the data measurement method.

```{r mutate2columns, echo=T, eval=T}
#  Add your name as a column and
#  some information about the method
scrap <- mutate(scrap, 
                scrap_finder    = "BB8",
                measure_method  = "REM-24")

## REM = Republic Equivalent Method
```


## Change a column  {-}
<hr class="hrlvl2">

Remember how the units of Tons was written two ways: "TONS" and "Tons"? We can use `mutate()` together with `tolower()` to make sure all of the scrap units are written in lower case. This will help prevent them from getting grouped separately in our plots and summaries.

```{r mutate-2000}
# Set units to all lower-case
scrap <- mutate(scrap, units = tolower(units))

# toupper() changes all of the letters to upper-case.
```


## Add calculated columns {-}

In our work we often use `mutate` to convert units for measurements. In this case, let's estimate the total pounds for the scrap items that are reported in tons. 


### Tons `to` Pounds conversion {-}

We can use `mutate()` to convert the `amount` column to pounds. Multiply the `amount` column by 2000 to get new values for a column named `amount_lbs`.

```{r, message=F, warning=F}
scrap_pounds <- mutate(scrap, amount_lbs = amount * 2000)
```

