
Use the `select()` function to:

- Drop columns you no longer need
- Pull-out a few columns to create a new table
- Rearrange or change the order of columns


## Drop columns with a minus sign: `-col_name` {-}
```{r select, warning = F, message = F}
library(dplyr)
library(readr)

scrap <- read_csv("https://itep-r.netlify.com/data/starwars_scrap_jakku.csv")

# Drop the destination column
select(scrap, -destination)
```


## Drop multiple columns {-}

Use `-c(col_name1, col_name2)` or `-col_name1, -col_name2` to drop multiple columns.

```{r select22, warning=F, message=F}

# Drop the destination and units columns
select(scrap, -c(destination, units, amount))
```


## Keep only 3 columns {-}
```{r arrange3, warning=F, message=F}
# Keep item, amount and price_per_pound columns
select(scrap, item, amount, price_per_pound)
```


## Select `everything()` else {-}

Select also works to change the order of columns. 
The code below puts the `item` column first and then moves the `units` and `amount` columns directly after `item`. 

We then keep `evertyhing()` else the same. 

```{r select44, warning = F, message = F}

# Make the `item`, `units`, and `amount` columns the first three columns
# Leave `everything()` else in the same order
select(scrap, item, units, amount, everything())
```

