
<details>
<summary class="btn_code_blue"> 
<span style="color: #f6cd00;"><i class="fas fa-star"></i></span> __Function options__ </summary>

<div class="note" style="margin-top: -10px;">
<p>
### Function options {-}

Functions have options —also called arguments— that change how they behave. You can set these optins using _arguments_. Let's look at a few of the arguments for the function `read_csv()`.

<br><br>

<h3> Skip a row </h3>

Sometimes you may want to ignore the first row in your data file, especially an EPA file that includes a disclaimer on the first row. Yes EPA, we're looking at you. Please stop.

Let's open the help window with `?read_csv` and try to find an argument that can help us. 

```{r, eval=F}
?read_csv
```

There's a lot of them! But the `skip` argument looks like it could be helpful. Take a look at the description near the bottom. The default is `skip = 0`, which reads every line, but we can skip the first line by writing `skip = 1`. Let's try.

```{r, eval=F}
read_csv("https://itep-r.netlify.com/data/starwars_scrap_jakku.csv", 
         skip = 1)
```


<h3> Limit the number of rows </h3>

Some types of data have last rows that show the _total_ or report "END OF DATA". In these cases we may want `read_csv` to ignore the last row of data, or for large data sets we may only want to pull in a 100 lines of data to see what you're working with. 

Let's look through the help window to find an argument that can help us. Type `?read_csv` and scroll down.

The `n_max` argument looks like it could be helpful. The default is `n_max = Inf`, which means it will read every line, but we can limit the lines we read to only one hundred by using `n_max = 100`.

```{r, eval=F}
# Read in 100 rows
small_data <- read_csv("https://mn-r.netlify.com/data/starwars_scrap_jakku.csv", 
                       skip = 1, 
                       n_max = 100)

# Remove the data
rm(small_data)

```


<h3> See function options </h3>

__To see all of a function's arguments__

- Type its name in the console followed by a parenthesis.
    - Type `read_csv( `
- Press `TAB` on the keyboard.
- Explore the drop-down menu of the available arguments. 

</p></div></details>


<div class="quiz">
<h3> Pop Quiz! </h3>

__Which of these is a valid function call?__

<input type="radio" name="func"> _fly(2 "ships")_                   <br> 
<input type="radio" name="func"> _find, "lightsaber", "Yoda"_       <br> 
<input type="radio" name="func"> _build(1000, "droids")_         <br> 
<input type="radio" name="func"> _wait(until   Empire    leaves)_     <br> 


<details>
<summary class = "btn_code">_Show solution_</summary>
<p>
<i class="fa fa-check" aria-hidden="true" style="color: green;"></i> `build(1000, "droids")`  

_Correct! You are ready to audit a Junk dealer._

</p>
</details>
</div>

