
## Bargain hunters {-}

Who's selling goods for cheap? Use `group_by` with the column _Origin_ to find the `mean(price_per_pound)` at each Origin City.

```{r mean_price-by-origin, eval = F}
scrap_means <- group_by(scrap, origin) %>%
                  summarize(mean_price =  mean(price_per_pound, na.rm = T))
```

<br>

<details>
<summary class="btn_code_blue"> Rounding digits </summary>
<div class="note" style="margin-top: -7px;">
<p>
### Rounding {-}

You can round the prices to a certain number of digits using the `round()` function. We can finish by adding the `arrange()` function to sort the table by our new column.

```{r mean_price-by-Origin-round, eval = F}
scrap_means <- scrap %>%
               group_by(origin) %>%
               summarize(mean_price       =  mean(price_per_pound, na.rm = T),
                         mean_price_round = round(mean_price, digits = 2)) %>%
               arrange(mean_price_round) %>%
               ungroup()
```

<br>


### Note {-}

The `round()` function in R does not automatically round values ending in 5 upwards. Instead it uses *scientific rounding*, which rounds values ending in 5 to the nearest **even** number. So 2.5 rounded to the nearest even number rounds down to **2**, and 3.5 rounded to the nearest even number rounds up **4**.

</p>
</div>
</details>


<br>

## Busiest scrap city {-}

So who's making the most transactions? Try using `group_by` with the column _origin_ to count the number of scrap records at each city. We can use the tiny-tiny function `n()` to count the number of rows.

```{r grp-by-origin, eval = FALSE}
scrap_counts <- scrap %>%
                group_by(origin) %>%
                summarize(origin_count = n()) %>%
                ungroup()
```

<br>

<div class="note">
### <i class="fas fa-hand-spock"></i> Spock-tip! {-}

Ending with `ungroup()` is good practice. This prevents your data from staying grouped after the summarizing has been completed.
</div>



# Save files
<hr>

Let's save the mean price table we created to a _CSV_. That way we can send it to Rey. To save a table we can use the `write_csv()` function from our favorite **readr** package. 

```{r, eval=F}
# Write the file to your results folder
write_csv(scrap_means, "results/prices_by_origin.csv")
```

<br>

<div class="red-note">
<h3 style="margin-top: 12px; color: white; margin-top: -6px; font-size: 22px;"><i class="fas fa-exclamation-triangle"></i> Note</h3>

By default, R will overwrite a file if the file already exists in the same folder. To be safe, save processed data to a new folder called `results/` and not to your raw `data/` folder.

</div>


# Grouped `mutate()` 
<hr>

We can bring back `mutate` to add a column based on the grouped values in a data set. For example, you may want to add a column showing the mean price by origin to the whole table, but still keep all of the records. This is a good way to add values to the table to serve as a reference point. 

> How does the price of **X** compare to the average price?   

When you combine `group_by` and `mutate` the new column will be calculated based on the values within each group. Let's group by `origin` to find the `mean()` price per pound at each origin. 


```{r mutate-price, eval=F}
scrap <- scrap %>%
         group_by( _______ ) %>% 
         mutate(origin_mean_price = mean(price_per_pound, na.rm = T)) %>% 
         ungroup()
```

<br>
