---
title: "My Analysis Outline"
output: 
  html_document:
    toc: false
    toc_depth: 2
    toc_float: true
    theme: readable
    highlight: tango
    number_sections: true
    self_contained: false
    fontsize: 18pt
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```


# Read data into R
```{r data}
library(readr)

# Read in a CSV file
air_data <- read_csv("data/OZONE_samples.csv")


# Have an EXCEL file?
## You can use read_excel() from the readxl package
install.packages(readxl)

library(readxl)

# Read in EXCEL file
air_data <- read_excel("data/OZONE_samples.xlsx")

```

# Plot the data
```{r view, message = F, fig.width=12, fig.height=4}
library(ggplot2)

#Remember the ggplot sandwich!
ggplot(air_data, aes(x = TEMP_F, y = OZONE)) + 
    geom_point(alpha = 0.2) +
    geom_smooth(method = "lm")
```


# Clean the data
```{r clean}
library(dplyr)

# Examples of common issues 

## Drop values out of range
air_data <- air_data %>% filter(OZONE > 0, TEMP_F < 199) 

## Convert all samples to PPB
air_data <- air_data %>% 
            mutate(OZONE = ifelse(UNITS == "PPM", OZONE * 1000, 
                                  OZONE)) 
```


# View the data again

Look at the data from different angles (e.g. by category, site, County, or facility). 

- The plotting function `facet_wrap()` is great for this.

```{r}
#
# Are some sites different?  
#
# We can facet the data by 'Site' to eliminate any noise 
# caused by mixing data from different sites, and learn 
# if the pattern between ozone and temperature varies.

ggplot(air_data, aes(x = TEMP_F, y = OZONE)) + 
    geom_point(alpha = 0.2, size = 3) +
    geom_smooth(method = "lm") + 
    facet_wrap(~SITE) +
    labs(title    = "Ozone increases with temperature", 
         subtitle = "Observations from 2015-2017")
```


# Summarize the data
```{r summary}
air_data <- air_data %>% 
            group_by(SITE, YEAR) %>% 
            summarize(AVG_OZONE = mean(OZONE) %>% round(2),
                      AVG_TEMP  = mean(TEMP_F) %>% round(2))
```


# Save the results

__Save the final data table__
```{r save-csv}
air_data %>% write_csv("results/2015-17_ozone_summary.csv")
```


<br>

__Save the plots__
```{r save-pdf, message=F}
ggsave("results/2015-2017 - Ozone vs Temp.pdf")
```



# Share it with the world

E-mail your script to all of your colleagues and create a github account [here](https://github.com/) to share your work with other R enthusiasts. 


## Congrats!!

<br><br>

