

Rey wants to know what the highest priced items are. Use `arrange()` to find the highest priced scrap item and see which origins might have a lot of them.

```{r arrange-price, warning = F}
# Arrange scrap items by price
scrap <- arrange(scrap, price_per_pound)

# View the top 6 rows
head(scrap)
```

<br>

>
> What, only `145 credits`!? That's not much at all. Oh wait...that's the smallest one on top. 
>


## Big things first: `desc()`  {-}

To arrange a column in descending order with the biggest numbers on top, we use: `desc(price_per_pound)`

```{r desc-arrange, warning = F}
# Put most expensive items on top
scrap <- arrange(scrap, desc(price_per_pound))

# View the top 8 rows
head(scrap, 8)
```


<br>

<div class="tip">
### <i class="fa fa-user-astronaut" style="color: green;"></i> Explore! {-}

Try arranging by more than one column, such as `price_per_pound` and `amount`. What happens?

__Hint:__ You can view the entire table by clicking on it in the upper-right _Environment_ tab.
</div>


<div class="yoda">
###  Yoda says {-}

When you save an arranged data table it maintains its order. This is perfect for sending people a quick __` Top 10 `__ list of pollutants or sites.

</div>

