
## New data -> New project! {-}

Below is an example workflow for an R project:

1. Create a new project
1. Read the data
1. Clean column names
1. Explore data
    - Plot the data
1. Clean the data
1. View the data closer
1. Summarize the data
1. Save the results
1. __Share__ with friends


### 0. Start a new project {-}

- Open a new project
- Open a new R script
- Create a `data` folder in your project directory 
- Copy your data to that folder


### 1. Read the data {-}
```{r data, message=F, warning=F}
library(readr)

# Read the file from your data folder
##air_data <- read_csv("data/OZONE_samples_demo.csv")

# Read the file from online
air_data <- read_csv("https://itep-r.netlify.com/data/OZONE_samples_demo.csv")
```


```{r tbl, echo=F}
library(knitr)
library(dplyr)

air_data %>% sample_n(5) %>% select(SITE, Date, OZONE, TEMP_F) %>% kable()
```


### 2. Clean column names {-}
```{r clean-names, message=F, fig.width=12, fig.height=4}
library(janitor)

# Capital letters and spaces make things more difficult
# Let's clean them out
air_data <- clean_names(air_data)
```


## 3.1 Explore the data {-}

> Hint: `summary()`, `glimpse()`, `nrow()`, `names()`
>

```{r glimpse, message=F}
# glimpse shows the firstfew records of every column
glimpse(air_data)
```



### 3.2 Plot the data {-}
```{r view, message=F, fig.width=12, fig.height=4}
library(ggplot2)

ggplot(air_data, aes(x = temp_f, y = ozone)) + 
  geom_point(aes(color = site), alpha = 0.4, size = 5)
```


### 4. Clean the data {-}
```{r clean, eval=T}
library(dplyr)

# Drop values out of range
air_data <- air_data %>% filter(ozone > 0, temp_f < 120) 

# Convert all samples to PPB
air_data <- air_data %>% 
            mutate(OZONE = ifelse(units == "PPM", ozone * 1000, 
                                  ozone)) 
```


### 5. View the data __closer__ {-}
```{r, fig.width=12, fig.height=4}
ggplot(air_data, aes(x = temp_f, y = ozone)) + 
    geom_point(alpha = 0.2, size = 3) +
    geom_smooth(method = "lm") + 
    facet_wrap(~site) +
    labs(title = "Ozone tends to increase with temperature", 
         subtitle = "Observations for 2015-2017",
         caption = "Source: MPCA air monitoring network")
```


> Keep exploring... 

### 6. Summarize the data {-}
```{r summary}
air_data <- air_data %>% 
            group_by(site, year) %>% 
            summarize(avg_ozone = mean(ozone) %>% round(2),
                      avg_temp  = mean(temp_f) %>% round(2))
```


```{r, echo=F}
air_data %>% kable()
```


###  7. Save the results {-}

__Save the data table__
```{r save-csv, eval=F}
write_csv(air_data, "results/2015_2017_ozone_summary.csv")
```


<br>
