
The first step of a good scrap audit is reading in some data to figure out where all the scrap is coming from. 
Here's a small dataset showing the scrap economy on Jakku. It was salvaged from a crash site, but the transfer was incomplete.

```{r ex-data1, echo=F, message=F, warning=F}
library(readr)
library(tibble)
library(knitr)

options(scipen = 999)

scrap <- data.frame(origin      = c("Outskirts", "Niima Outpost", "Cratertown", "Tro----"), 
                    destination = c("Raiders", "Trade caravan", "Plutt", "Ta----"), 
                    item        = c("Bulkhead", "Hull panels", "Hyperdrives", "So---*"), 
                    amount      = c(332, 1120, 45, 1), 
                    price_d     = c("300", "286", "45", "10----"))

kable(scrap)
```


This looks like it could be useful. Now, if only we had some more data to work with...

## New Message _(1)_ {-}

<details>
<summary class = "btn_code_green">_Incoming..._ _BB8_</summary>
<p>

<div class="tip">
__BB8:__ _Beep boop Beep._

__BB8:__ _I intercepted a large scrapper data set from droid 4P-L of Junk Boss Plutt._   

<br>

Receiving data now...

<br>

__scrap_records.csv__ 

```{r, eval=F}
item,origin,destination,amount,units,price_per_pound  
Flight recorder,Outskirts,Niima Outpost,887,Tons,590.93  
Proximity sensor,Outskirts,Raiders,7081,Tons,1229.03  
Aural sensor,Tuanul,Raiders,707,Tons,145.27  
Electromagnetic filter,Tuanul,Niima Outpost,107,Tons,188.2  
...  
```

<br>

__You:__ _Yikes! This looks like a mess! What can I do with this?_

</div>
</p></details>


## CSV to the rescue {-}

The main data format used in R is the __CSV__ _(comma-separated values)_. A __CSV__ is a simple text file that can be opened in R and most other stats software, including Excel. It looks squished together as plain text, but that's okay! When opened in R, the text becomes a familiar looking table with columns and rows. 

Before we launch ahead, let's add a _package_ to R that will help us read __CSV__ files.

<br>

<details>
<summary class = "btn_code_blue"> How to save a CSV from Excel </summary>
<p>
<div class="note">


__Step 1:__ Open your Excel file.

__Step 2:__  Save as CSV

- Go to _File_  
- _Save As_  
- _Browse_ to your project folder  
- Save as type: _CSV (Comma Delimited) (*.csv)_  
    - Any of the _CSV_ options will work    
- Click __Yes__      
- Close Excel (Click "Don't Save" as much as you need to. Seriously, we just saved it. Why won't Excel just leave us alone?)    

__Step 3:__ Return to RStudio and open your project. Look at your _Files_ tab in the lower right window. Click on the _CSV_ file you saved and choose __View File__. 

__Success!__

<br>

</div></p></details>

<br>
